Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-04-21 paper2_JNLS/paper.tex
NM

%----------------------------------------------------------------------------%
%% LATEX DEFINITIONS
%----------------------------------------------------------------------------%
% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\nick}[1]{{\color{red} #1}}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
\newcommand{\eps}{\varepsilon}
\newcommand{\dx}{\, dx}
\newcommand{\CC}{{\mathbb{C}}}

@@

\todo[inline]{Need to cite \cite{onorato2016origin} as recommended by ref 1 and maybe \cite{onorato2016twenty} which was not recommended by a referee, but is more specific to KdV}

@@

Inserting \eqref{H3convert} and \eqref{H2convert} into \eqref{H3H2ratio}, and using the definitions of $C_2$ and $C_3$ from \eqref{C3C2}, gives the remarkably explicit formula
\begin{equation}
\label{SkewPred}
\frac{\skwdn(\eta)} {\vardn(\eta_x) - \varup(\eta_x)} = \frac{1}{3} \epsup^{-3} \dratdn^3 
%= \frac{1}{3} \left( \frac{\ddn}{\etastd} \right)^3
\end{equation}
This formula links the skewness of the outgoing wave field to the change in the variance of surface slope. In particular, it predicts their ratio to scale as the {\em inverse cube of wave amplitude}, $\epsup^{-3}$, and the {\em cube of the depth ratio}, $\dratdn^3$. It is a rather unexpected relationship, as it would have been difficult to anticipate that the displacement skewness and slope variance, among all possible variable combinations, are so intimately related.

>>>>

%----------------------------------------------------------------------------%
%% LATEX DEFINITIONS
%----------------------------------------------------------------------------%
% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\nick}[1]{{\color{red} #1}}
\newcommand{\new}[1]{{\color{blue} #1}}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
\newcommand{\eps}{\varepsilon}
\newcommand{\dx}{\, dx}
\newcommand{\CC}{{\mathbb{C}}}

@@

@@

Inserting \eqref{H3convert} and \eqref{H2convert} into \eqref{H3H2ratio}, and using the definitions of $C_2$ and $C_3$ from \eqref{C3C2}, gives the remarkably explicit formula
\begin{equation}
\label{SkewPred}
\frac{\skwdn(\eta)} {\vardn(\eta_x) - \varup(\eta_x)} = \frac{1}{3} \epsup^{-3} \dratdn^3 
%= \frac{1}{3} \left( \frac{\ddn}{\etastd} \right)^3
\end{equation}
This formula links the skewness of the outgoing wave field to the change in the variance of surface slope. In particular, it predicts their ratio to scale as the {\em inverse cube of wave amplitude}, $\epsup^{-3}$, and the {\em cube of the depth ratio}, $\dratdn^3$. It is a rather unexpected relationship, as it would have been difficult to anticipate that the displacement skewness and slope variance, among all possible variable combinations, are so intimately related.
%
\new{We remark that Eq.~\eqref{SkewPred} bears similarity to a formula derived by Onorato \& Suret \cite{onorato2016twenty} in the context of {\em constant-depth} KdV that relates the skewness to the spectral bandwidth. A similar formula relates kurtosis to spectral bandwidth in the context of the nonlinear Schr{\"o}dinger equation \cite{onorato2016origin}. Indeed, to leading order $\eta_t = c \eta_x$, so that $c^2 \var(\eta_x)$ can be approximated by the spectral bandwidth $\var(\eta_t)$ in Eq.~\eqref{SkewPred}. We note that these earlier works considered only {\em constant} depth situations, where changes in spectral bandwidth, and the associated changes in skewness/kurtosis arose from out-of-equilibrium initial conditions. In contrast, the present study....
}

\vsp{4}
\new{The present study derives a formula for changing depth, in contrast to the simpler situation of constant depth where changes in spectral bandwidth arise from out-of-equilibrium initial conditions, as considered in \cite{onorato2016twenty, onorato2016origin}}

%\todo[inline]{Need to cite \cite{onorato2016origin} as recommended by ref 1 and maybe \cite{onorato2016twenty} which was not recommended by a referee, but is more specific to KdV}
